Finding Maximum $k$-Cliques Faster using Lazy Global Domination

### 2016-04-08 paper/paper.tex
Marketing

We introduced a new lazy global domination rule. This was sometimes extremely beneficial---without
this rule, we would have been unable to solve six of the problem instances we considered, and many
others would have taken much longer. However, even with laziness there is still sometimes a cost to
pay when this rule does nothing. This rule is thus harmful for the graphs typically considered for
the maximum clique problem, and we see the benefit of tailoring algorithms to the problem being
solved. We suggest that a similar rule may also be useful for the maximum $k$-club problem.

>>>>

We introduced a new lazy global domination rule. This was sometimes extremely beneficial, leading to
exponential reductions in the search space---without this rule, we would have been unable to solve
eight of the problem instances we considered, and many others would have taken much longer. However,
even with laziness there is still sometimes a cost to pay when this rule does nothing. This rule is
thus harmful (although only by a polynomial factor) for the graphs typically considered for the
maximum clique problem, and we see the benefit of tailoring algorithms to the problem being solved.
We suggest that a similar rule may also be useful for the maximum $k$-club problem.
